Acid-induced protein gels: from gelation to stress-induced failure

### 2015-06-04 talk_Zurich.tex
Texture as important as taste

>>>>

\begin{frame}{Texture as important as taste}
\begin{tikzpicture}[inner sep=0, callout pointer segments=3]
\node(ishichan) {\includegraphics[height=8\baselineskip]{ishichan}};
\node[above=of ishichan] {\includegraphics[height=8\baselineskip]{calamar}};
\node[cloud callout,anchor=west, draw, callout relative pointer={(-30:2\baselineskip)}] at ($(ishichan.north)+(-0.5\textwidth,0)$) {\includegraphics[height=5\baselineskip]{aldente}};
\node[cloud callout, aspect=0.75, anchor=east, draw, callout relative pointer={(-150:2\baselineskip)}] at ($(ishichan.north)+(0.5\textwidth-10pt,0)$) {\includegraphics[height=5\baselineskip]{chewie}};
\end{tikzpicture}
\end{frame}
